surfing

### 2022-09-26 inst/surfing_jsa_rebuttal_minorcomments.tex

Page 3: Change ``Further, we use a generalization due to (Luce,
1959)..." to ``Further, we use a generalization due to Luce
(1959)...".

Page 7: Change ``..., but in addition we may reject the
the proposal that..." to ``..., but in addition we may reject the
proposal that...".

\textcolor{blue}{Done}

Page 10: References with URL's should be split over multiple lines to avoid being cut-off the page.

Page 11: Table 1 could be formatted to fit within the page margins.

Page 17: Capitalisation of Figure 2 axis titles.

Page 17: Figure 2 caption is a little brief and could better explain
what is observed in the plot (e.g. the positive correlation between
variables). Especially as the authors have distorted the x-axis and
fitted a linear trend through the data. What is the reason for this?
As mentioned in a previous comment, I’d prefer to see the x-axis in
its raw form, unless there is a reason it has been distorted.

\textcolor{blue}{More detail added in caption}

Page 18: Figure 3 title – this doesn’t provide the reader with any
additional information. It does seem a little odd that Figure 2 does
not have a title, Figure 3 does, and Figure 4 does not. For
consistency, the authors could simply remove the title from Figure 33,
as it does not really add any value.

Page 19: Figure 4 Capitalisation of y-axis title.  General comment:
should the Table and Figure captions have a full-stop at the end of
the last sentence?

General comment
As part of a potential future publication in the field, I’d be curious to see the methodology in Section
7 applied to World Surf League data from events that occurred prior to the announcement that surfing
would be in the Olympics. Comparing these results with those in the paper that use data from after
this announcement (perhaps supplemented with additional data and results from post-2019), would
help in our understanding whether there truly has been an observable change in non-competitive
behaviour between compatriots. Any such analysis is clearly well beyond the realm of minor revisions
and is not something I expect of the authors prior to final submission; however, I thought it could be
an interesting next step for the application of the methodology outlined in the paper!

### 2022-09-26 inst/surfing.Rmd
fixes #179

```{r plotwidep}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype wide",ylab="support")
abline(h= -2,lty=2)
pdf(file="plotwidep.pdf")
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Bradley-Terry strength of the Brazilian beachtype reified entity",ylab="support")
abline(h= -2,lty=2)
dev.off()
```

>>>>

```{r plotwidep}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype wide",ylab="support")
abline(h= -2,lty=2)
pdf(file="plotwidep.pdf")
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Bradley-Terry strength of the Brazilian beachtype reified entity",ylab="Support")
abline(h= -2,lty=2)
dev.off()
```
